%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%% \usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\usepackage{url}

% footer page number
\usepackage{fancyhdr}
\pagestyle{fancy}

\fancyhf{}
\fancyheadoffset{0cm}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\thepage}
\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyfoot[C]{\thepage}%
}
% end of footer page number

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------
% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket
% two addresses
\def\@tablebox#1{\begin{tabular}[t]{@{}l@{\extracolsep{\fill}}}#1\end{tabular}}
\begingroup{
  \leavevmode\hbox to \textwidth{\hfil\@tablebox{\namefont{Xu Cui}}\hfil}\par
  \leavevmode\hbox to \textwidth{
    \@tablebox{
      % left address
      {\bf Local Address} \\ Apt 911 - 137 University Ave. \\ Waterloo, ON. N2L 3E6 \\ (226)-989-1171
    }\hfil
    \@tablebox{
      % middle information: used \hspace to make it look better
      \\ \hspace{-5mm} \url{https://cs.uwaterloo.ca/~xcui/} \\
      \hspace{7mm} xcui@uwaterloo.ca
    }\hfil
    \@tablebox{
      % right address
      {\bf Permanent Address} \\ 532 Kilbirnie Drive \\ Ottawa, ON. K2J 5R7 \\ (613)-565-0352
    }
  }\par

}\endgroup
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%% \section{\centerline{OBJECTIVE}}

%% \vspace{8pt} % Gap between title and text

%% A position in Personnel Administration utilizing skills in recruiting, training and compensation.\\


%----------------------------------------------------------------------------------------
%	Personal Summary SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Personal Summary}}

\vspace{15pt} % Gap between title and text

\begin{itemize} \itemsep -2pt % Reduce space between items
\item I am a PhD Candidate at the David R. Cheriton School of Computer Science, University of Waterloo
  under the supervision of Professor Bernard Wong and Professor Khuzaima Daudjee.
\item My research interests include distributed systems, cloud storage systems, and software-defined networks.
\end{itemize}

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Summary OF Qualificiations SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Summary of Qualifications}}
\vspace{15pt} % Gap between title and text

\begin{itemize} \itemsep -2pt % Reduce space between items
% year count started sing Sept 2011 where I worked with Professor Li Ming
\item 5 years' experience in designing, implementing, evaluating and fine-tuning large scale software systems
\item Strong leadership in project management; strong analytical skills; years of expertise in problem solving
\item Strong programming skills in C++, JavaScript, Python, Ruby, Racket, Java; expertise in MySQL, PostgreSQL and MongoDB; experience in Linux administration and Amazon Web Services
\item Consistently recognized by supervisors/managers as a very systematic, competent and highly motivated individual
\item Excellent verbal and written communication skills to achieve team goals; solid expertise in summarizing and presenting research to colleagues and supervisors; fluent reading and writing skills in English and Chinese
\item Consistently able to deliver results under tight deadlines, highly motivated, and very systematic
\end{itemize}

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Education SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Education}}

\vspace{8pt} % Gap between title and text

{\sl PhD, Computer Science} \\
University of Waterloo, Waterloo, Ontario \hfill September 2015 -- present\\
GPA: 94/100 \\
Milestones completed: Comprehensive I, January 2016.

{\sl Master of Mathematics}, Computer Science  \\
University of Waterloo, Waterloo, Ontario
\hfill  October 2015\\
Thesis ``Leveraging Software-Defined Networking to Improve Distributed Transaction Processing Performance'',
October, 2015\\
GPA 92/100

{\sl Bachelor of Computer Science}, with Distinction \\
University of Waterloo, Waterloo, Ontario \hfill June 2013\\
Major Average: 92/100

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Publications}}

\vspace{15pt} % Gap between title and text
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Akshay K. Singh, \textbf{Xu Cui}, Benjamin Cassell, Bernard Wong, and Khuzaima Daudjee, \textit{MicroFuge: A Middleware Approach to Providing Performance Isolation in Cloud Storage Systems.} In Proceedings of the International Conference on Distributed Computing Systems (ICDCS), Madrid, Spain, June 2014.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Technical Reports SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{Technical Reports}}

\vspace{15pt} % Gap between title and text
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Sharon Choy, Bernard Wong, \textbf{Xu Cui}, and Xiaoyi Liu, \textit{CrossStitch: An Efficient Transaction
  Processing Framework for Geo-Distributed Systems.} University of Waterloo, School of Computer Science Technical Report CS-2015-08, June 2015.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Presentations SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{Presentations}}

\vspace{15pt} % Gap between title and text
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Poster Presentation of \textit{MicroFuge: A Middleware Approach to Providing Performance Isolation in Cloud Storage Systems} at Cheriton Research Symposium, Waterloo Canada, September 19, 2014.
\item Conference Presentation of \textit{MicroFuge: A Middleware Approach to Providing Performance Isolation in Cloud Storage Systems} at the 34th International Conference on Distributed Computing Systems (ICDCS), Madrid Spain, July 2014.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Awards and Scholarships SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{Awards and Scholarships}}
\vspace{15pt} % Gap between title and text
\begin{itemize} \itemsep -2pt % Reduce space between items
\item 2018-2019 (expected). GO-bell Scholarship, University of Waterloo.
  \hspace*{\fill} CAD 10,000/year
\item 2016-2018 David R. Cheriton Graduate Scholarship, University of Waterloo.
  \hspace*{\fill} CAD 10,000/year
\item 2015-2017. Ontario Graduate Scholarship.
  \hspace*{\fill} CAD 15,000/year
\item 2015-2017. President's Graduate Scholarship, University of Waterloo.
  \hspace*{\fill} CAD 10,000/year
\item 2013-2015. David R. Cheriton Graduate Scholarship, University of Waterloo.
  \hspace*{\fill} CAD 10,000/year
\item 2014. International Conference on Distributed Computing Systems Travel Grant.
  \hfill USD 1,100

\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Research Experience SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Research Experience}}

\vspace{8pt} % Gap between title and text

{\sl Research Assistant} \\
University of Waterloo, Waterloo, Ontario \hfill September 2013 -- present
\begin{itemize} \itemsep -2pt % Reduce space between items
% year count starts in September 2013
\item Contributed to four research projects, ShiftFit, NetStore, CrossStitch, and MicroFuge, as well a web application project DataMagic over a period of 2 years.
\item Chief architecture for NetStore, a high performance network-aware distributed transaction processing system. NetStore leverages software-defined networking to improve transaction response times by as much as 77\% while doubling the throughput in event of high network utilization. Implemented about 10,000 lines of system code in C++ and Java in a period less than 8 months.
\item Evaluated CrossStitch, a new transaction processing framework, by co-designing and co-implementing the TPC-C benchmark using the transaction interface provided by CrossStitch. Designed and deployed a fully automated testbed framework for CrossStitch.
\item Led the DataMagic Project, a cloud based data analytics system which collects, analyzes and visualizes data available from public sectors (e.g. Police/Fire Departments, Hydro etc.). Designed and implemented the prototype of the DataMagic system with colleagues. Co-designed a set of RESTful APIs, which can provide unified, structured data to interested parties.
\item Evaluated, designed and implemented the caching and scheduling algorithms of
  MicroFuge, a middleware which provides performance isolation in cloud environments, which improved MicroFuge’s existing performance by more than 50\%. Drove the MicroFuge project at full speed to achieve both high performance and quality standards under a tight deadline.
\item Acquired valuable experience in system evaluation and tuning techniques.
\item In charge of the setups and fine-tuning of distributed development and testing
  environments on various cloud platforms from different providers.
\end{itemize}

\vspace{-6pt} % Reduce space between positions at the same organization

{\sl Undergraduate Research Assistant} \\[2pt]
University of Waterloo, Waterloo, Ontario \hfill September 2011 -- April 2013
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed and implemented the fundamental natural language parsing engine of RSVP, a
  Natural Language Processing Engine created to answer questions in natural languages.
\item Engineered and built the data collection engine of RSVP used to provide structured data
  in response to questions.
\item Constructed and developed an Android Library for potential customers to utilize the
  Natural Language Processing Engine.
\item Gained experience in natural language processing techniques, data collection methods,
  and database technologies.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Teaching Experience}}

\vspace{8pt} % Gap between title and text
{\sl Instructional Apprentice} for CS136 -- Elementary Algorithm Design and Data Abstraction \\
University of Waterloo, Waterloo Ontario\hfill Winter 2014, Spring 2014, Fall 2014, and Winter 2015
\begin{itemize} \itemsep -2pt
\item Instruct weekly tutorial.
\item Research and create tutorial material.
\item Provide one to one help to students during office hours.
\end{itemize}
%% \vspace{-9pt}
{\sl Teaching Assistant}
\begin{itemize} \itemsep -2pt
\item CS136 --  Elementary Algorithm Design and Data Abstraction  \hfill Winter 2014, Fall 2014
\item CS230 -- Introduction to Computers and Computer Systems \hfill Fall 2013, Fall 2015
\item CS241 -- Foundations of Sequential Programs \hfill Winter 2016, Spring 2016
\item CS350 -- Operating Systems \hfill Spring 2015
\item CS454 -- Distributed Systems \hfill Spring 2015
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Volunteer Experience SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Volunteer Experience}}

\vspace{15pt} % Reduce space between section title and contents

\begin{itemize} \itemsep -2pt
\item Exploiting Text Workshop Volunteer, Waterloo Canada \hfill August 7 -- 8, 2014.
\item CS4U DAY Volunteer, Waterloo Canada \hfill December 7, 2015.
  \vspace{-7pt} % Reduce space between section title and contents
  \begin{itemize} \itemsep -2pt
  \item Presented a research poster, which was created as a graduate course deliverable, to visiting high school students.
  \end{itemize}
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Services SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Services}}

\vspace{15pt} % Reduce space between section title and contents

\begin{itemize} \itemsep -2pt
\item External Reviewer, ACM Symposium on Cloud Computing, SoCC. 2015, 2016.
\item External Reviewer, IEEE International Conference on Distributed Computing Systems, ICDCS. 2015.
\item External Reviewer, International Conference on Database Systems for Advanced Applications, DASFAA. 2014.
\item External Reviewer, European Conference on Computer Systems, EuroSys. 2014.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Interests SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{Interests}}

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Spending time with my family, reading, mountain climbing, cooking
\end{center}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
